Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-06-09 supplement.tex
back-to-Africa migration

>>>>

\subsection{Back-to-Africa Gene flow and Neanderthal ancestry in Africa}

Back-to-Africa migrations likely introduced Neanderthal ancestry into Africa \cite{Chen2020}. This Neanderthal ancestry would cause reticulation in the ancestry of the African populations, and is therefore relevant to the modelling presented here. Our models do account for both Neanderthal admixture out of Africa and Back-to-Africa migrations, such that they predict the amount of Neanderthal ancestry that we would expect to find in African individuals. We find that the MSL are predicted to carry \sgcomment{TODO} $XX-YY \%$ Neanderthal ancestry, which is remarkably consistent with the results of \cite{Chen2020}. Since the IBD statistics from \cite{Chen2020} are not used in the present analysis, this serves as an independent validation of the present models. More importantly, since the Neanderthal admixture in Africa is properly accounted for in the model, we do not expect the presence of such ancestry to bias our estimate of reticulation in Africa.
